---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rappdirs

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-lib/rappdirs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/rappdirs/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/rappdirs/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/rappdirs?branch=main)
<!-- badges: end -->

`rappdirs` is a port of [appdirs](https://github.com/ActiveState/appdirs) to R.
It lets you find the appropriate directory to save caches, logs, and data, on Linux, Mac, and Windows.
It allows you to store files that need to shared across R sessions in a way that aligns with the [CRAN policies](https://cran.r-project.org/web/packages/policies.html).

## Motivation

What directory should your app use for storing user data?
If running on Mac OS X, you should use:

    ~/Library/Application Support/<AppName>

If on Windows (at least English Win XP) that should be:

    C:\Documents and Settings\<User>\Application Data\Local Settings\<AppAuthor>\<AppName>

or possibly:

    C:\Documents and Settings\<User>\Application Data\<AppAuthor>\<AppName>

for [roaming profiles](https://docs.microsoft.com/en-us/previous-versions/windows/it-pro/windows-vista/cc766489(v=ws.10)) but that is another story.

On Linux (and other Unices) the dir, according to the [XDG spec](https://specifications.freedesktop.org/basedir-spec/basedir-spec-latest.html) (and subject to some interpretation), is either:

    ~/.config/<AppName>     

or possibly:

    ~/.local/share/<AppName>

## Usage

This kind of thing is what rappdirs is for.
rappdirs will help you choose an appropriate:

-   user data dir (`user_data_dir()`)
-   user config dir (`user_config_dir()`)
-   user cache dir (`user_cache_dir()`)
-   site data dir (`site_data_dir()`)
-   user log dir (`user_log_dir()`)

For example, on Mac:

```{r}
library(rappdirs)
appname <- "SuperApp"
appauthor <- "Acme"
user_config_dir(appname, appauthor)
user_data_dir(appname, appauthor)
site_data_dir(appname, appauthor)
user_cache_dir(appname, appauthor)
user_log_dir(appname, appauthor)
```
